Strings methods analysis

### 2022-08-19 article.tex
extrapolation method simplified

    To solve this problem we propose to use probabilistic approach. Suppose we need to know how many times a method with name Y has been used on string. Randomly gather a sample of files where this word Y occurs. Analyze what percentage of them uses word Y as a string method. Also find out the total number of times word Y was used in the code. Multiplying the total number by the probability we will get the answer.
    In fact, we will apply the extrapolation method.

>>>>

    To solve this problem we can apply the extrapolation method here.
